---
title: "Affirmative Action in College Admission: Readers' Response to Supreme Court Decision"
subtitle: "Topic Modeling of NYT and WSJ Online Comments"
author: "Asif Mehedi | Darden School"
date: 2024-05-10
execute: 
  warning: false
format:
  html:
    toc: true
    number-sections: true
    colorlinks: true
    code-overflow: scroll
    code-fold: true
    section-divs: true
    backgroundcolor: cornsilk
    code-line-numbers: true
    code-block-border-left: true
    link-external-icon: true
    link-external-newwindow: true
    footnotes-hover: true
    lang: en-US
---

::: {.callout-tip}
To view, change or execute any code, or to add your own, please open the source notebook (a .qmd file) in R Studio. You'll need to install the Quarto CLI tool .

A R script version of this notebook is also available in the repository.

If you're reading this on a webpage, the codeblocks are collapsed by default. To expand a codeblock, click on `▶ Code`. 
:::


::: {.callout-note}
## About Quarto Notebook
This document was written as a [Quarto](https://quarto.org/) notebook, which provides a rich authoring and publishing environment. Importantly, the notebook format allows the interleaving of prose commentary and code outputs (such as tables or plots) between blocks of code. It's also easy to convert a notebook to a range of formats.
:::

First we load the R packages we'll use in this exercise.

```{r}
#| echo = false

library(tidyverse) # A collection of packages for data processing https://www.tidyverse.org/
library(topicmodels) # LDA https://cran.r-universe.dev/topicmodels
library(tm) # various "text mining" tasks https://r-forge.r-universe.dev/tm
# library(wordcloud)
library(stopwords) # lists of common words https://quanteda.r-universe.dev/stopwords
library(ldatuning) # find optimal number of topics https://nikita-moor.r-universe.dev/ldatuning
# possible use
# https://bstewart.r-universe.dev/stm structural topic model
```


To avoid ambiguity, I use the general term `post` to mean top-level comments as well as nested replies. I reserve the term `comment` to mean only top-level comments.


```{r}
en_stopwords <- stopwords::stopwords(
    language = "en", source = "snowball"
)
```

# How many topics?

See the references mentioned at the end of [this vignette](https://rpubs.com/siri/ldatuning).
